Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-03-25 manuscript/manuscript.Rnw
use the linage table explanation text

\begin{table}
  \footnotesize
<<primate.lineage.specific,echo=FALSE,results="asis">>=
pri.all.lin.spec <- placenta.lineage.specific.table("pri.all")
setkey(pri.all.lin.spec,"Human Symbol")
@ 
\caption{Genes whose expression changed significantly in the primate
  order as compared to all other analyzed species.}
\label{tab:primate_lineage_specific}
\end{table}

@@

\begin{table}
  \footnotesize
<<human.lineage.specific,echo=FALSE,results="asis">>=
hum.all.lin.spec <-
    placenta.lineage.specific.table("hum.all",
                                    lineage.table=human.mouse.lineage.specific.analysis,
                                    members=40)
setkey(hum.all.lin.spec,"Human Symbol")
@ 
\caption{Genes whose expression changed significantly in \human
  as compared to all other analyzed species.}
\label{tab:human_lineage_specific}
\end{table}

@@

We examined the expression of three rodents, \mouse, \carmeli, and
\galili{}. We did not detect any significant changes on the Rodentia
lineage in comparison to all other analyzed species (Supplemental
\cref{tab:rodentia_lineage_specific}), likely because of a lack power
to overcome multiple testing.

>>>>

\begin{table}
  \footnotesize
<<primate.lineage.specific,echo=FALSE,results="asis">>=
pri.all.lin.spec <- placenta.lineage.specific.table("pri.all")
setkey(pri.all.lin.spec,"Human Symbol")
@ 
\caption{\linagetableexplanation{primates}}
\label{tab:primate_lineage_specific}
\end{table}

@@

\begin{table}
  \footnotesize
<<human.lineage.specific,echo=FALSE,results="asis">>=
hum.all.lin.spec <-
    placenta.lineage.specific.table("hum.all",
                                    lineage.table=human.mouse.lineage.specific.analysis,
                                    members=40)
setkey(hum.all.lin.spec,"Human Symbol")
@ 
\caption{\lineagetableexplanationtypeiii{\human}{all other analyzed species}}
\label{tab:human_lineage_specific}
\end{table}

@@

We examined the expression of three rodents, \mouse, \carmeli, and
\galili{}. We did not detect any significant changes on the Rodentia
lineage in comparison to all other analyzed species (Supplemental
\cref{tab:rodentia_lineage_specific}), likely because of a lack power
to overcome the multiple testing correction. Additional species and/or
samples in each of these lineages will be necessary to detect lineage
specific shifts.

### 2016-03-25 manuscript/supplemental_material.Rnw
use the linage table explanation text

\begin{table}[hb]
  \footnotesize
<<human.lineage.specific,echo=FALSE,results="asis">>=
hum.all.lin.spec <- placenta.lineage.specific.table("hum.all")
setkey(hum.all.lin.spec,"Human Symbol")
@ 
\caption{Genes whose expression changed in \human
  as compared to all other analyzed species.}
\label{tab:human_lineage_specific}
\end{table}

\begin{table}[hb]
  \footnotesize
<<rodentia.lineage.specific,echo=FALSE,results="asis">>=
rod.all.lin.spec <- placenta.lineage.specific.table("rod.all")
setkey(rod.all.lin.spec,"Human Symbol")
@ 
\caption{Genes whose expression changed in the Rodentia
  order as compared to all other analyzed species.}
\label{tab:rodentia_lineage_specific}
\end{table}

\begin{table}[hb]
  \footnotesize
<<lau.lineage.specific,echo=FALSE,results="asis">>=
lau.all.lin.spec <- placenta.lineage.specific.table("lau.all")
setkey(lau.all.lin.spec,"Human Symbol")
@ 
\caption{Genes whose expression changed in the Laurasiatheria
  superorder as compared to all other analyzed species.}
\label{tab:laurasiatheria_lineage_specific}
\end{table}

\begin{table}[hb]
  \footnotesize
<<eua.lau.lineage.specific,echo=FALSE,results="asis">>=
eua.lau.lin.spec <- placenta.lineage.specific.table("eua.lau")
setkey(eua.lau.lin.spec,"Human Symbol")
@ 
\caption{Genes whose expression changed between the
  Euarchontoglires and Laurasiatherian superorder.}
\label{tab:laurasiatheria_euarchontoglires_lineage_specific}
\end{table}

>>>>

\begin{table}[hb]
  \footnotesize
<<rodentia.lineage.specific,echo=FALSE,results="asis">>=
rod.all.lin.spec <- placenta.lineage.specific.table("rod.all")
setkey(rod.all.lin.spec,"Human Symbol")
@ 
\caption{\lineagetableexplanation{the rodentia order}{all other species}}
\label{tab:rodentia_lineage_specific}
\end{table}

\begin{table}[hb]
  \footnotesize
<<lau.lineage.specific,echo=FALSE,results="asis">>=
lau.all.lin.spec <- placenta.lineage.specific.table("lau.all")
setkey(lau.all.lin.spec,"Human Symbol")
@ 
\caption{\lineagetableexplanation{the laurasiatheria
    superorder}{all other species}}
\label{tab:laurasiatheria_lineage_specific}
\end{table}

\begin{table}[hb]
  \footnotesize
<<eua.lau.lineage.specific,echo=FALSE,results="asis">>=
eua.lau.lin.spec <- placenta.lineage.specific.table("eua.lau")
setkey(eua.lau.lin.spec,"Human Symbol")
@ 
\caption{\linagetableexplanation{ the euarchontoglires superorder}{ the laurasiatherian superorder}}
\label{tab:laurasiatheria_euarchontoglires_lineage_specific}
\end{table}
